The paper on blockchain front-running

### 2018-09-21 frontrunning/Latex/sections/paper.tex
more changes

The concept of  \emph{front-running} is decades old starting with early financial markets. Initially, the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change. Clearly, in such scenarios front-running was possible yet not detectable as a damaging activity. However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore, a new form of front-running is feasible through high-speed networks. Furthermore, Blockchain technology has introduced transparency and open markets and leads to a new era of front-running which inherently affects all decentral applications, whether financial or non-financial. Arbitrage and Censorship, are also issues that have been linked to front-running attacks on blockchain \textit{(We need to talk about why these two are left out of the scope of this paper)}. Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} Using this criteria, we successfully categorized these decentral applications into 4 principal categories on which we conduct our analysis. Surprisingly, there was no ICO (initial coin offering) included in the top 25 DApps list by the time we fetched the data from the website. We believe the reason is that the ICOs are inherently different from other groups of Daaps as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over. Therefore, we  consider ICOs as other cases on which the front-running should be investigated (although they are not listed in the top 25 DApps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}

@@

%______________________________________________________________%
\section{Preliminaries}

@@

\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
%As traditional front-running has been the subject of discussion for decades, there are many works of literature on this subject. Here we focus on the historical context and how the regulations evolved to be what they are today.\\
Front-running was first observed on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by Securities Exchange Commission \textit{(SEC)} in 1977 as:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}
\end{quote}

@@

Blockchain technology has received an exceptional amount of attention since it was first introduced as the underlying technology of the cryptocurrency Bitcoin in 2008~\cite{nakamoto2008bitcoin}. Many decentralized applications that are built on top of this technology represent the significance of the blockchain as it completely eliminates the central point of failure within the systems. However, blockchains have some inherent characteristic that leaves them vulnerable to information leaks and \emph{front-running} behaviour. Although this data structure is known to be publicly visible to every network participants, information is layered and some of them are easier accessed only by insiders. Any network participants that runs a full node on the blockchain is able to obtain that information and as mentioned in section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front-running. %Decentralized exchanges are a group of blockchain financial applications where front-running can be executed. 
%____________________________________________________________________
%%% The following chunk seem to be redundant and weird. Should we keep it?? 
Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from the potential price increase of the market stocks (details are provided in~\ref{sec:frontrunningExchanges}). Decentralized namespaces, as blockchain non-financial applications, are another example. Ethereum Name Service and Ghazal \cite{moosavighazal} are such systems in which upon seeing a transaction from Alice to register \texttt{alice.eth}, front-runner can go ahead of her and register this domain name. He can later sell \texttt{alice.eth} to Alice for a higher price and profit.
Another application that is vulnerable to front-running is Initial Coin Offering (ICO) smart contracts. ICO is a method to distribute tokens based on the deposits of the native coin, Ether in the case of Ethereum. After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico, li2018initial}. ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.  This competition made ICOs a good opportunity for front-running attacks.  In this paper, we use multiple empirical examples to show the possibility of front-running on DApps. For the sake of completeness, we use one incident on ICOs, and examples from the Top 25 DApps by recent user counts based on \texttt{DAppRadar.com} ranking. 
%____________________________________________________________________

@@

Due to the novelty characteristics of the underlying technology (blockchain), there are only a few research carried out on the issue of front-running in the context of blockchain and decentral ledgers. \\
Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}. As mentioned in section~\ref{sec:What is front-running?}, the information leakage results in the entire system to be vulnerable to the front-running. They also propose a cryptographic approach, similar to commit and reveal(~\ref{CommitmentScheme}), to prevent front-running in decentral systems. %In this approach, which is similar to commit and reveal, a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information. Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast. This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.
Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers~\cite{malinova2017market}. They argue that blockchain brings new options of transparency which affects traders behaviour, especially in the presence of intermediary front-runners. They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient.

Breidenbach~\etal~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts. Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter. In order to mitigate this issue they proposed \textit{Submarine Commitments} which we discuss further in section~\ref{submarineCommits}.

One of the properties of Blockchain technology was to overcome double-spend, however, this does not apply for fast payments and zero-confirmation transactions. \textit{Double-spend attack}, as the name implies, the adversary spends a coin more than one time. To do so, he would use the coin as an input of a transaction and broadcast it to the network, before the transaction gets validated and executed, he broadcasts another transaction associated with a higher transaction fee which spends the same input~\cite{bamert2013have, karame2012double}. This adversarial behaviour is similar to the front-running attack where the attacker front-runs his own transaction by paying a higher fee when broadcasting the second transaction.

@@

%______________________________________________________________%
\subsection{Name Services.}

>>>>

Blockchain technology enables smart contracts or decentralized applications (DApps). Function calls (or transactions) to the DApp are processed by a decentralized network. Transactions are finalized in stages: they (generally) first relay around the network, then are selected by a miner and put into a valid block, and finally the block is well-enough incorporated that is unlikely to be reorganized. Front-running is an attack where a malicious node observes a transaction after it is broadcast but before it is finalized, and attempts to have its own transaction confirmed before or instead of the observed transaction. Whether this attack is beneficial depends on the logic of the DApp itself.

In this paper, we perform a number of case studies of DApps on Ethereum (a popular blockchain supporting DApps) that are volnerable to front-running attacks. We draw the cases from the top 25 most active DApps,\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} as well as ICOs which are absent from this list during a sampling period. xxx tend to appear on this list when they are actively issued.      benefit of this attack varies on what the DApps is doing but, this attack .

%The concept of  \emph{front-running} is decades old starting with early financial markets. Initially, the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change. Clearly, in such scenarios front-running was possible yet not detectable as a damaging activity. However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore, a new form of front-running is feasible through high-speed networks. Furthermore, Blockchain technology has introduced transparency and open markets and leads to a new era of front-running which inherently affects all decentral applications, whether financial or non-financial. Arbitrage and Censorship, are also issues that have been linked to front-running attacks on blockchain \textit{(We need to talk about why these two are left out of the scope of this paper)}. Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} Using this criteria, we successfully categorized these decentral applications into 4 principal categories on which we conduct our analysis. Surprisingly, there was no ICO (initial coin offering) included in the top 25 DApps list by the time we fetched the data from the website. We believe the reason is that the ICOs are inherently different from other groups of Daaps as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over. Therefore, we  consider ICOs as other cases on which the front-running should be investigated (although they are not listed in the top 25 DApps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}

As a preview, in Section~\ref{sec:frontrunningExchanges}), we examine Bancor~\cite{hertzog2017bancor}, a decentralized exchange that operates similar to traditional stock markets and is likewise volunerable to front-running. Domain name frontrunning occurs when a user uses a domain registrar to inquire if a domain is available for purchase, and the query triggers the registrar to purchase the domain in anticipation that it can sell it to the user. In Section~\ref{sec:ens}, we examine decentralized namespaces like Ethereum Name Service and academic works like Ghazal~\cite{moosavighazal} where relaying nodes and miners see Alice's attempt to purchase a domain name before it is finalized in a block. A front-running node might try to supersede her transaction. In Section~\ref{sec:ICOsfrontrunning}, we look at Initial Coin Offerings (ICOs). After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico, li2018initial}. ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}. We show empirical evidence of a miner purchasing tokens ahead of other users.

@@

%______________________________________________________________%
\section{Preliminaries \& Related Work}

@@

\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
%As traditional front-running has been the subject of discussion for decades, there are many works of literature on this subject. Here we focus on the historical context and how the regulations evolved to be what they are today.\\
Front-running was first observed on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by Securities Exchange Commission \textit{(SEC)} in 1977 as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}''

@@

In one sense, blockchain technology (which was introduced via Bitcoin in 2008~\cite{nakamoto2008bitcoin}) strives to disintermediate certain central parties that would participate in a transaction. However, blockchains also introduce new participants in the relaying and finalization (\ie mining) of transactions. Any network participant that runs a full node on the blockchain is able to obtain proposed transactions before they are added to the blockchain and miners are free in the transactions they select for inclusion in their attempted blocks. This can leave blockchain applications vulnerable to front-running, as we will see through the several case studies detailed in this paper.

%____________________________________________________________________

@@

Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}.They also propose a cryptographic approach, similar to commit and reveal (see Section~\ref{CommitmentScheme}) to prevent front-running.
%As mentioned in section~\ref{sec:What is front-running?}, the information leakage results in the entire system to be vulnerable to the front-running.  %In this approach, which is similar to commit and reveal, a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information. Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast. This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.
Malinova and Park discuss different design settings for financial markets and trading platforms on decentralized ledgers~\cite{malinova2017market}. They argue that blockchain brings new options of transparency which affects traders behaviour, especially in the presence of intermediary front-runners. They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient. Breidenbach~\etal~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts. Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter. In order to mitigate this issue they proposed \textit{Submarine Commitments} which extend commit and reveal; we discuss them further in Section~\ref{submarineCommits}.

Double-spending attacks in Bitcoin have been studied~\cite{bamert2013have, karame2012double} where a user broadcasts a transaction and is able to obtain some off-blockchain good or service before the transaction has actually been (fully) confirmed. The user can then broadcast a competing transaction that sends the same unspent coins to herself, perhaps using higher transaction fees, arrangements with miners, or artefacts of the network topology to have the second transaction confirmed instead of the first. We think of this as a type of front-running.

In the cryptographic literature, front-running attacks are modelled by allowing a `rushing' adversary to interact with the protocol. In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running. Literature like the Bitcoin Backbone~\cite{} and Hawk~\cite{} capture this.

%\textblue{Equate front-running to a rushing adversary in the crypto literature and cite the fact that UC models of blockchains capture front-running attacks: cite Bitcoin Backbone paper and Hawk paper in particular.}

@@

%______________________________________________________________%
\subsection{Name Services.}\label{sec:ens}
